### 2016-06-08 capability-machine.tex
Make the document compile with my pdflatex.
Updated reg-file relation and expression relation to only consider pc. Updated the value relation according
Updated the FTLR to be consistent with update to expression relation

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{thmtools}
\usepackage{stmaryrd}
\usepackage{natbib}
\usepackage{url}
\usepackage{array}
\usepackage{arydshln}
\usepackage{ifthen}

@@

\begin{align*}
  \readCond{n,W,\start,\addrend} = & \;\exists r \in \RegionName \ldotp \\
                                   & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nsubeq[n-1] \iota_{\start',\addrend'} \\ & \\
  \writeCond{n,W,\start,\addrend} = & \; \exists r \in \RegionName \ldotp \\
                                   & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nequal[n-1] \iota_{\start',\addrend'} \\
  \execCond{n,W,\start,\addrend} = & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                   & \; \quad \forall \npair[n']{v_1},\dots,\npair[n']{v_k} \in \stdvr(W'),\addr' \in [\start, \addrend] \ldotp \\
                                   & \; \qquad \npair[n']{[\pcreg \mapsto (\exec,\start,\addrend,\addr'), r_1 \mapsto v_1, \dots , r_k \mapsto v_k]} \\
                                   & \; \qquad \quad \in \stder(W') \\
  \entryCond{n,W,\start,\addrend,\addr} = & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                   & \; \quad \forall \npair[n']{v_1},\dots,\npair[n']{v_k} \in \stdvr(W') \ldotp \\
                                   & \; \qquad \npair[n']{[\pcreg \mapsto (\exec,\start,\addrend,\addr), r_1 \mapsto v_1, \dots , r_k \mapsto v_k]} \\
                                   & \; \qquad \quad \in \stder(W') \\
\end{align*}
\stdvr \; : \;  \Worlds \monfun \UPred{\Words}
  \stdvr(W) \defeq & \{ \npair{i} \mid i \in \ints \} 
\union \\
                   & \{ \npair{\stdcap[\noperm] }  \} 
\union \\
                   & \{ \npair{\stdcap[\readonly] } \mid \readCond{n,W,\start,\addrend} \} \union \\
%                   & \quad \exists r \in \RegionName \ldotp \\
%                   & \qquad  \forall \addr \in \{\start, \dots, \addrend \} \ldotp \\
%                   & \qquad \quad  \forall \npair{\heapseg} \in W(r)(W)\ldotp \\
%                   & \qquad \qquad   \addr \in \dom(\heapseg) \land \\
%                   & \qquad \qquad   \npair[n-1]{\heapseg(\addr)} \in \stdvr(W)\} 
                   & \{ \npair{\stdcap[\readwrite] } \mid \writeCond{n,W,\start,\addrend} \} \union \\
%                   & \quad \exists r \in \RegionName \ldotp \\
%                   & \qquad  \forall \addr \in \{\start, \dots, \addrend \} \ldotp \\
%                   & \qquad \quad  \forall \npair{\heapseg} \in W(r)(W)\ldotp \\
%                   & \qquad \qquad   \addr \in \dom(\heapseg) \land \\
%                   & \qquad \qquad   \npair[n-1]{\heapseg(\addr)} \in \stdvr(W) \land \\
%                   & \qquad \qquad   \forall n' < n, W' \future W, v \ldotp \\
%                   & \qquad \qquad \quad \heapSat{n'}{W'} \land \\
%                   & \qquad \qquad \quad \npair[n']{v} \in \stdvr(W') \\
%                   & \qquad \qquad \qquad  \Rightarrow \exists W'' \future W' \ldotp \heapSat[\memheap\update{a}{v}]{n''}{W''} \}
                   & \{ \npair{\stdcap[\exec]} \mid \\
                   & \quad\readCond{n,W,\start,\addrend} \land \\
%                   & \quad (\exists r \in \RegionName \ldotp \\
%                   & \qquad  \forall \addr \in \{\start, \dots, \addrend \} \ldotp \\
%                   & \qquad \quad  \forall \npair{\heapseg} \in W(r)(W)\ldotp \\
%                   & \qquad \qquad   \addr \in \dom(\heapseg) \land \\
%                   & \qquad \qquad   \npair[n-1]{\heapseg(\addr)} \in \stdvr(W)) \\
                   & \quad \execCond{n,W,\start,\addrend} \}
%                   & \quad (\forall n' < n \ldotp \forall W' \future W \ldotp \\
%                   & \qquad \forall \npair[n']{v_1,\dots,v_k} \in \stdvr(W'),\addr' \in \{\start, \dots, \addrend \} \ldotp \\
%                   & \qquad \quad \npair[n']{[\pcreg \mapsto (\exec,\start,\addrend,\addr'), r_1 \mapsto v_1, \dots , r_k \mapsto v_k]} \in \stder(W')) \}
\union \\
% For the entry case a capability is acceptable, if we can change it to an execute permission and put it as the pc and we otherwise have valid words in the registers, then the register file should be valid.
                   & \{ \npair{\stdcap[\entry]} \mid \entryCond{n,W,\start,\addrend} \} \union \\
%                   & \quad \forall n' < n \ldotp \forall W' \future W \ldotp \\
%                   & \qquad \forall \npair[n']{v_1,\dots,v_k} \in \stdvr(W') \ldotp \\
%                   & \qquad \quad \npair[n']{[\pcreg \mapsto \stdcap[\exec], r_1 \mapsto v_1, \dots , r_k \mapsto v_k]} \in \stder(W') \}
                   & \{ \npair{\stdcap[\rwx] = c} \mid \\
                   & \quad \writeCond{n,W,\start,\addrend} \land \\
                   & \quad \execCond{n,W,\start,\addrend} \}
%                   & \quad \exists r \in \RegionName \ldotp \\
%                   & \qquad  \forall \addr \in \{\start, \dots, \addrend \} \ldotp \\
%                   & \qquad \quad  \forall \npair{\heapseg} \in W(r)(W)\ldotp \\
%                   & \qquad \qquad   \addr \in \dom(\heapseg) \land \\
%                   & \qquad \qquad   \npair[n-1]{\heapseg(\addr)} \in \stdvr(W) \land \\
%                   & \qquad \qquad   \forall n' < n, W' \future W, v \ldotp \\
%                   & \qquad \qquad \quad \heapSat{n'}{W'} \land \\
%                   & \qquad \qquad \quad \npair[n']{v} \in \stdvr(W') \\
%                   & \qquad \qquad \qquad  \Rightarrow \exists W'' \future W' \ldotp \heapSat[\memheap\update{a}{v}]{n''}{W''} \\
%                   & \quad \land \\
%                   & \quad \forall n' < n \ldotp \forall W' \future W \ldotp \\
%                   & \qquad \forall \npair[n']{v_1,\dots,v_k} \in \stdvr(W'),\addr' \in \{\start, \dots, \addrend \} \ldotp \\
%                   & \qquad \quad \npair[n']{[\pcreg \mapsto (\exec,\start,\addrend,\addr'), r_1 \mapsto v_1, \dots , r_k \mapsto v_k]} \in \stder(W') \}

@@

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat[\heap]{n'}{W'}, \npair{v_1 \dots v_k} \in \stdvr(W') \ldotp \\
                   & \qquad \quad (n,[\pcreg \mapsto \updatePcPerm{c},r_0 \mapsto v,r_1 \mapsto v_1,\dots, r_k \mapsto v_k], \heap) \in \observations(W) \}
\end{align*}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stder(W) \defeq & \{ \npair{\reg} \mid \\
                   & \quad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad  \forall \heapSat[\heap]{n}{W}, \heap_f \ldotp \\
                   & \qquad \quad (n,\reg\update{r_0}{c},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}
Register-file relation:
\begin{align*}
  \stdgr \quad : & \quad \Worlds \monfun \UPred{\Regs} \\
  \stdgr(W) \defeq & \{ \npair{\reg} \mid \\
                    & \quad \forall r \in \RegName \ldotp \\
                    & \qquad  \npair{\reg(r)} \in \stdvr(W) \}
\end{align*}

@@

\end{definition}
\begin{lemma}[Fundamental theorem of logical relations (FTLR)] \forcenewline
  For any $n \in \nats$, $W \in \Worlds$, and register file $\reg$, if  $\npair{\reg} \in \stdgr(W)$, then $(n,\reg) \in \stder(W)$
\end{lemma}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{thmtools}
\usepackage{stmaryrd}
\usepackage{natbib}
\usepackage{url}
\usepackage{array}
\usepackage{arydshln}
\usepackage{ifthen}
\usepackage{ifpdf}

@@

\begin{align*}
  \readCond{n,W,\start,\addrend} =        & \;\exists r \in \RegionName \ldotp \\
                                          & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nsubeq[n-1] \iota_{\start',\addrend'} \\ & \\
  \writeCond{n,W,\start,\addrend} =       & \; \exists r \in \RegionName \ldotp \\
                                          & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nequal[n-1] \iota_{\start',\addrend'} \\ & \\
  \execCond{n,W,\start,\addrend,\perm} =  & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                          & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
                                          & \; \qquad \npair{(\perm,\start,\addrend,\addr)} \in \stder(W') \\ & \\
  \entryCond{n,W,\start,\addrend,\addr} = & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                          & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(W') \\
\end{align*}

\[
\stdvr \; : \;  \Worlds \monfun \UPred{\Words}
\]
\begin{align*}
  \stdvr(W) \defeq & \{ \npair{i} \mid i \in \ints \} 
\union \\
                   & \{ \npair{\stdcap[\noperm] }  \} 
\union \\
                   & \{ \npair{\stdcap[\readonly] } \mid \readCond{n,W,\start,\addrend} \} \union \\
                   & \{ \npair{\stdcap[\readwrite] } \mid \writeCond{n,W,\start,\addrend} \} \union \\
                   & \{ \npair{\stdcap[\exec]} \mid \\
                   & \quad\readCond{n,W,\start,\addrend} \land \\
                   & \quad \execCond{n,W,\start,\addrend,\exec} \}
\union \\
% For the entry case a capability is acceptable, if we can change it to an execute permission and put it as the pc and we otherwise have valid words in the registers, then the register file should be valid.
                   & \{ \npair{\stdcap[\entry]} \mid \entryCond{n,W,\start,\addrend} \} \union \\
                   & \{ \npair{\stdcap[\rwx] = c} \mid \\
                   & \quad \writeCond{n,W,\start,\addrend} \land \\
                   & \quad \execCond{n,W,\start,\addrend,\exec} \land \\
                   & \quad \execCond{n,W,\start,\addrend,\rwx} \}
\end{align*}

@@

Register-file relation:
\begin{align*}
  \stdgr \quad : & \quad \Worlds \monfun \UPred{\Regs} \\
  \stdgr(W) \defeq & \{ \npair{\reg} \mid \\
                    & \quad \forall r \in \RegName \setminus \{\pcreg\} \ldotp \\
                    & \qquad  \npair{\reg(r)} \in \stdvr(W) \}
\end{align*}

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat[\heap]{n'}{W'} \ldotp \forall \reg \in \stdgr(W') \\
                   & \qquad \quad (n,reg\update{r_0}{v}\update{\pcreg}{\updatePcPerm{c}}, \heap) \in \observations(W) \}
\end{align*}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder(W) \defeq & \{ \npair{\pc} \mid \\
                   & \quad \forall \reg \in \stdgr(W) \ldotp \\
                   & \qquad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad \quad  \forall \heapSat[\heap]{n}{W}, \heap_f \ldotp \\
                   & \qquad \qquad (n,\reg\update{r_0}{c}\update{\pcreg}{\pc},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}

@@

\end{definition}
\begin{lemma}[Fundamental theorem of logical relations (FTLR)] \forcenewline
  For any $n \in \nats$, $W \in \Worlds$, and a word $\pc$, if  $\npair{\pc} \in \stdvr(W)$, then $\npair{\pc} \in \stder(W)$
\end{lemma}
